A thermodynamic view of dusty protoplanetary disks: axisymmetric stability

### 2016-10-19 linear.tex
re-written thermo interpret section

\section{Compressible streaming instability} 
In the special case of an unstratified disk (neglecting the vertical
component of the stellar gravity), we may also Fourier analyze in $z$
to obtain a local dispersion relation of the form  
$\sum_{j=1}^{5}c_j(k_x,k_z)\sigma^j = 0$, where $k_z$ is a real
vertical wavenumber. The coefficients $c_j$ can be read 
off Eq. \ref{streaming_dispersion} in  Appendix \ref{compressible_streaming}. 
There we also show that this dispersion relation reduces to that for
the streaming instability in the limit of incompressible gas and small
$\tstop$ \citep{youdin05a,jacquet11}.

>>>>

\section{Compressible streaming instability}\label{si}
In the special case of an unstratified disk (neglecting the vertical
component of the stellar gravity), we may also Fourier analyze in $z$
to obtain a local dispersion relation of the form  
$\sum_{j=1}^{5}c_j(k_x,k_z)\sigma^j = 0$, where $k_z$ is a real
vertical wavenumber. The coefficients $c_j$ can be read 
off Eq. \ref{streaming_dispersion} in  Appendix \ref{compressible_streaming}. 
There we also show that this dispersion relation reduces to that for
the streaming instability in the limit of incompressible gas and small
$\tstop$ \citep{youdin05a,jacquet11}.

### 2016-10-19 model.tex
minor updates
re-written thermo interpret section

The gas component of the mixture has an entropy that is not conserved 
because of the (locally) isothermal equation of state 
adopted. However, we can define an effective (dimensionless)
entropy for the \emph{entire mixture} as 
\begin{align}
   \seff \equiv \ln \frac{P}{\rho} = \ln{\left[c_s^2(1-\tepsilon)\right]}.  
\end{align} 
We shall see that by defining an effective entropy this way, many of the 
results concerning the stability of dusty gas will have identical form
and interpretations to that in standard adiabatic hydrodynamics of 
pure gas. For example, if $c_s^2$ is constant and $\tstop=0$, then
$D\seff/ D t = 0$ since $D\tepsilon/D t=0$ in that case.

@@

In this section we review the basic properties of the 
single-fluid mixture using Eqs.\ref{masseq}--\ref{momeq} with 
Eq. \ref{eff_energy} in place of the dust continuity equation. Our
discussion is based on the corresponding axisymmetric linearized
equations. A variable $f$ is
subject to Eulerian perturbations of the form 
\begin{align}
 \real\left[ \delta f(r,z)\exp{\left(-\ii\sigma t\right)}\right], 
\end{align}
where $\sigma$ is the complex mode frequency. In Appendix
\ref{var_prin} we derive the integral relation,  
\begin{align}
&  \sigma^2\int\rho\left(|\dd v_r|^2 + |\dd v_z|^2\right)dV \notag\\
&= \int\left[ \rho
  |\dd v_r|^2A + \rho  \dd v_z \dd v_r^* B + \rho \dd v_z^*\dd v_r C +
  \rho |\dd v_z|^2 D\phantom{\frac{1}{1}}\right. \notag\\
&\phantom{===}  \left. + \frac{1}{P}\Bigl\lvert \nabla\cdot\left(P\dd
  \bm{v}\right)\Bigr\rvert^2\right]dV  -\int \left(\nabla\cdot\dd\bm{v}^*\right)\dd\mathcal{C}dV \notag\\
&\phantom{===}
- \int P
  \left(\nabla\cdot\dd\bm{v}^*\right)\left(\dd\bm{v}\cdot\nabla\ln{c_s^2}\right)dV.\label{int_rel}
\end{align} 
The real coefficients $A,B,C,D$ can be read off 
Eq. \ref{integral_ex}. Note that $B=C$ from dynamical equilibrium
(Eq. \ref{vshear}). We now consider various limits of
Eq. \ref{int_rel}.

@@

In this case, the last two integrals in Eq. \ref{int_rel} vanish. Then 
requiring $\sigma^2>0$  gives the criteria 
for the axisymmtric \emph{stability} of an isothermal gas perfectly 
coupled to dust,  
\begin{align}
  \kappa^2 + c_s^2 \nabla\ln{\rhog}\cdot\nabla\tepsilon &> 0,\label{dusty_solberg1}  \\
  -c_s^2\frac{\p\ln{\rhog}}{\p z}\left(-\kappa^2\frac{\p\tepsilon}{\p
    z} + r\frac{\p\Omega^2}{\p z}\frac{\p \tepsilon}{\p r} \right) & > 0, \label{dusty_solberg2}
\end{align} 
%\begin{align}
%  \kappa^2 - \frac{1}{\rho}\nabla P \cdot \nabla s &> 0, \label{dusty_solberg1}    \\
%  -\frac{1}{\rho}\frac{\p P}{\p z} \left(\kappa^2 \frac{\p s}{\p z} -
%  r\frac{\p\Omega^2}{\p z}\frac{\p s}{\p r}\right) &>0, \label{dusty_solberg2}
%\end{align} 
where %$s = \ln{P/\rho}$, 
$\kappa^2 \equiv r^{-3}\p_r\left(r^4\Omega^2\right)>0$ is the 
square of the epicylic frequency. %We assume $\kappa^2>0$.  
Eq. \ref{dusty_solberg1}---\ref{dusty_solberg2} are in fact the 
the Solberg-Hoiland criteria for axisymmetric stability of adiabatic
gas if one inserts $C_p\ln{\left(1 -
    \tepsilon\right)}$ for the entropy in the standard
expression for said criteria \citep[e.g.][ where $C_p$ is the heat
  capacity]{tassoul78}.

@@

\subsection{Thermodynamics of dust-drag instabilities}\label{dust_work}
Now consider constant $c_s$ but $\tstop\neq0$. 
%When $c_s(r,z)$ is non-uniform but $\tstop=0$, 
Eq. \ref{int_rel} indicates that $\sigma^2$ is generally complex, so
we may have growing oscillations. Writing $\sigma = -\omega + \ii s$
where $\omega$ and $s$ are the real frequency and growth rates, 
respectively, the imaginary part of Eq. \ref{int_rel} gives 
\begin{align}
  s = \frac{\imag\int \left(\nabla\cdot\dd\bm{v}^*\right)\dd\mathcal{C}dV}{2\omega\int\rho\left(|\dd
    v_r|^2 + |\dd v_z|^2\right)dV}, \label{thermal_instability}
\end{align}
which represent instabilities due to dust-gas friction. 
Since drag ($\delta \mathcal{C}$) appears as a source term in our
effective energy equation, the quantity 
$\imag\left[\left(\nabla\cdot\dd\bm{v}^*\right)\dd\mathcal{C}\right]$
may be thought of as a correlation between compression/expansion and  
heating/cooling.

It is well-known that such correlations can lead to pulsational
instabilities in stars \citep{cox67}. One may thus interpret 
dust-drag instabilities in a similar way. We give a
qualitative 
description below, adapted from the more rigorous treatments of stellar 
pulsations by 
\cite{cox67} and lecture notes by \cite{samadi15} and
J. Christensen-Dalsgaard\footnote{\url{http://astro.phys.au.dk/$\sim$jcd/oscilnotes/}}.

@@

The Lagragian perturbation $\Delta$ of a variable $f$ is 
related to its Eulerian perturbation by $\Delta f = \delta f + 
\bm{\xi}\cdot\nabla f$; where $\bm{\xi}$ is the Lagragian  
displacement ($    \xi_{x,z} =  \ii \dd v_{x,z}/\sigma$). 
%Note that $\Delta
%\mathcal{C} = \delta \mathcal{C}$ for a uniform background $C$ as
%required for equilibrium. 
Then Eq. \ref{lin_mass_full}---\ref{lin_energy_full} imply  
\begin{align} 
  \imag \left(\delta \mathcal{C}
  \nabla\cdot\dd \bm{v}^*\right) = 
  -|\sigma|^2\imag \left(\Delta P 
  \frac{\Delta\rho^*}{\rho}\right), \label{pdv}
\end{align}
which states that `PdV' work (right hand side) is
provided by dust-drag friction. This can be seen explicitly as
follows.

The average rate of work done by the dusty-gas is
\begin{align}
  \mathcal{W} = \frac{1}{T_p}\int^{t+T_p}_{t}dt^\prime\int_M P
  \frac{Dv}{Dt^\prime} dm 
\end{align}
\citep{cox67}, 
where $T_p$ is the oscillation period, $v=1/\rho$ is the specific
volume of the mixture, and the spatial integral is taken over the
total mass $M$ of the mixture and $dm$ is the mass element.

Our aim is to relate the work done by the mixture, $\mathcal{W}$, 
to the growth rate of oscillation amplitudes, $s$. To do this, we
first evaluate $\mathcal{W}$ assuming pure oscillations (perturbations
with time dependence $e^{\ii\omega t}$ and real $\omega$), then show
that in fact the amplitudes grow if the work done is positive.

Noting that only products in the perturbations contribute to 
$\mathcal{W}$, we find that for real $\omega$: 
\begin{align}
  \mathcal{W} = - \frac{\omega}{2} \int \imag\left(\Delta P
  \frac{\Delta \rho^*}{\rho}\right)dV,\label{work_real}
\end{align}
where the integral is taken over the volume of the
mixture. Eq. \ref{work_real} show that a phase difference between
pressure and density leads to work done.

Now combining Eq. \ref{work_real}, \ref{pdv} and \ref{thermal_instability}
gives  
\begin{align}
s = \frac{2}{\mathcal{I}^2}\mathcal{W}, \label{growth_work}
\end{align}
where $\mathcal{I}^2>0$  is the integral in the denominator of
Eq. \ref{thermal_instability}, and we have set $\sigma= - \omega$ in
Eq. \ref{pdv} for pure oscillations.  Thus growing modes in fact arise if
positive work is done by the mixture during an oscillation. This in
turn requires pressure to lag density, discussed next.

\subsubsection{Physical picture of dust-drag instabilities} 
The full energy equation is 
\begin{align*}
  \frac{DP}{Dt} = \frac{P}{\rho}\frac{D\rho}{D t} + \mathcal{C}. 
\end{align*}
Dust-drag causes a phase difference between the pressure and density 
evolution of a fluid element. In Fig. \ref{pdv_cartoon}, we show that
if pressure lags behind density, then positive
work done ($\mathcal{W}>0$) and would lead to growing oscillations
($s>0$).

\begin{figure}
  \includegraphics[width=\linewidth]{figures/drag}\\
\includegraphics[width=\linewidth]{figures/pdv}
  \caption{Thermodynamic interpretation of overstable modes caused by
    dust-gas drag. Top: pressure and density evolution in time. 
    Bottom: oscillation cycle in the $P$-$V$ plane. In the case shown,
    dust-drag causes 
    pressure to lag behind density, which results in a clockwise path in
    the $P$-$V$ plane, implying positive work done by the fluid and
    hence would lead to growing oscillation amplitudes.  
    \label{pdv_cartoon}
  }
\end{figure}

Consider a fluid element at maximum density during an oscillation cycle
(point $A$), so that $D\rho/ D t = 0$. If dust-gas drag provides an
effective heating to the fluid element at $A$ (i.e. gas influx)  then
it will experience increasing pressure, $DP/D t>0$. It attains
pressure maximum (point $B$) \emph{after} reaching density maximum.   
This implies pressure maximizes while the parcel is expanding: 
the parcel's path in the `$P$-$V$' plane  is clockwise, as shown in
the bottom panel of Fig. \ref{pdv_cartoon}. This corresponds to
positive work done.

Our thermodynamic interpretation does not explain
\emph{why} dust drag causes a pressure lag behind density, but merely shows
that this \emph{must} be the case for any growing modes associated the
dust drag. To rigorously understand how dust-drag causes this lag requires an
explicit solution to the linearized equations with detailed treatment
of the function $\mathcal{C}$. However, given the complexity of
$\mathcal{C}$ (see Appendix \ref{lin_dust}), we might generally expect
the dusty disks to  support a range of stable and unstable modes, with the
latter being associated with pressure-density lag.

Indeed, \cite{jacquet11} explains the essence of the streaming 
instability in dusty protoplanetary disks as dust accumulation
(and hence compression) at a pressure bump, which then drags the 
gas towards it (and hence heating) to strengthen the pressure
bump. That is, heating occurs upon compression, as occurs for stellar 
pulsational instabilities. A phase difference was also noted in the 
numerical calculations of the streaming instability by 
\citet{youdin07b}.

@@

\subsection{Locally isothermal gas perfectly coupled to dust}\label{dusty_vsi_int}
If $c_s(r,z)$ is non-uniform but $\tstop=0$, Eq. \ref{int_rel} 
gives  
\begin{align}
  s = \frac{\imag\int P
  \left(\nabla\cdot\dd\bm{v}^*\right)\left(\dd\bm{v}\cdot\nabla\ln{c_s^2}\right)dV}{2\omega\int\rho\left(|\dd
    v_r|^2 + |\dd v_z|^2\right)dV}. \label{vsi_check}
\end{align} 
This is VSI caused by vertical shear arising from a radial
temperature gradient \citep{nelson13,barker15,lin15}. We present 
numerical solutions of the VSI with perfectly-coupled dust in \S\ref{results}.

>>>>

The gas component of the mixture has a specific entropy
$S = C_p\ln{P/\rhog^\gamma}$, where $C_p$ is the heat capacity at constant
pressure. However, this is not a useful quantity for (locally)
isothermal gas.

Nevertheless, since we have shown that an isothermal dusty gas
effectively has $\gamma=1$ we can define an effective (dimensionless)  
entropy for the \emph{entire mixture} as 
\begin{align}
   \seff \equiv \ln \frac{P}{\rho} = \ln{\left[c_s^2(1-\tepsilon)\right]}.  
\end{align} 
We shall see that by defining an effective entropy this way, many of the 
results concerning the stability of dusty gas will have identical form
and interpretations to that in standard adiabatic hydrodynamics of 
pure gas. For example, if $c_s^2$ is constant and $\tstop=0$, then
$D\seff/ D t = 0$ since $D\tepsilon/D t=0$ in that case.

@@

In this section we review the basic properties of the 
single-fluid mixture using Eqs.\ref{masseq}--\ref{momeq} with 
Eq. \ref{eff_energy} in place of the dust continuity equation. Our
discussion is based on the corresponding axisymmetric linearized
equations. A variable $f$ is
subject to Eulerian perturbations of the form 
\begin{align}
 \real\left[ \delta f(r,z)\exp{\left(-\ii\sigma t\right)}\right], 
\end{align}
where $\sigma$ is the complex mode frequency. In Appendix
\ref{var_prin} we derive the integral relation,  
\begin{align}
%&  \sigma^2\int\rho\left(|\dd v_r|^2 + |\dd v_z|^2\right)dV \notag\\
  \sigma^2\mathcal{I}^2
&= \int\left[ \rho
  |\dd v_r|^2A + \rho  \dd v_z \dd v_r^* B + \rho \dd v_z^*\dd v_r C +
  \rho |\dd v_z|^2 D\phantom{\frac{1}{1}}\right. \notag\\
&\phantom{===}  \left. + \frac{1}{P}\Bigl\lvert \nabla\cdot\left(P\dd
  \bm{v}\right)\Bigr\rvert^2\right]dV  -\int \left(\nabla\cdot\dd\bm{v}^*\right)\dd\mathcal{C}dV \notag\\
&\phantom{===}
- \int P
  \left(\nabla\cdot\dd\bm{v}^*\right)\left(\dd\bm{v}\cdot\nabla\ln{c_s^2}\right)dV.\label{int_rel}
\end{align} 
The real integral $\mathcal{I}^2>0$ and coefficients $A,B,C,D$ can be
read off Eq. \ref{integral_ex}. %Note that $B=C$ from dynamical equilibrium
%(Eq. \ref{vshear}). 
We now consider various limits of Eq. \ref{int_rel}.

@@

In this case, the last two integrals in Eq. \ref{int_rel} vanish. Then 
requiring $\sigma^2>0$  gives the criteria 
for the axisymmtric \emph{stability} of an isothermal gas perfectly 
coupled to dust,  
\begin{align}
  \kappa^2 + c_s^2 \nabla\ln{\rhog}\cdot\nabla\tepsilon &> 0,\label{dusty_solberg1}  \\
  -c_s^2\frac{\p\ln{\rhog}}{\p z}\left(-\kappa^2\frac{\p\tepsilon}{\p
    z} + r\frac{\p\Omega^2}{\p z}\frac{\p \tepsilon}{\p r} \right) & > 0, \label{dusty_solberg2}
\end{align} 
%\begin{align}
%  \kappa^2 - \frac{1}{\rho}\nabla P \cdot \nabla s &> 0, \label{dusty_solberg1}    \\
%  -\frac{1}{\rho}\frac{\p P}{\p z} \left(\kappa^2 \frac{\p s}{\p z} -
%  r\frac{\p\Omega^2}{\p z}\frac{\p s}{\p r}\right) &>0, \label{dusty_solberg2}
%\end{align} 
where %$s = \ln{P/\rho}$, 
$\kappa^2 \equiv r^{-3}\p_r\left(r^4\Omega^2\right)>0$ is the 
square of the epicylic frequency. %We assume $\kappa^2>0$.  
Eq. \ref{dusty_solberg1}---\ref{dusty_solberg2} are in fact the 
the Solberg-Hoiland criteria for axisymmetric stability of adiabatic
gas if one inserts $C_p\ln{\left(1 -
    \tepsilon\right)}$ for the entropy in the standard
expression for said criteria \citep[e.g.]{tassoul78}.

@@

\subsection{Thermodynamics of dust-drag instabilities}\label{dust_work}
Now consider constant $c_s$ but $\tstop\neq0$. 
Eq. \ref{int_rel} indicates that $\sigma^2$ is generally complex, so
we may have growing oscillations (overstability). Writing $\sigma =
-\omega + \ii s$ where $\omega$ and $s$ are the real frequency and
growth rates, respectively, the imaginary part of Eq. \ref{int_rel}
gives  
\begin{align}
%  s = \frac{\imag\int \left(\nabla\cdot\dd\bm{v}^*\right)\dd\mathcal{C}dV}{2\omega\int\rho\left(|\dd
%    v_r|^2 + |\dd v_z|^2\right)dV}, \label{thermal_instability}
  s = \frac{\imag\int \left(\nabla\cdot\dd\bm{v}^*\right)\dd\mathcal{C}dV}{2\omega\mathcal{I}^2}. \label{thermal_instability}
\end{align}
This represents instability due to dust-gas friction. 
Since drag ($\delta \mathcal{C}$) appears as a source term in our
effective energy equation, the quantity 
$\imag\left[\left(\nabla\cdot\dd\bm{v}^*\right)\dd\mathcal{C}\right]$
may be thought of as a correlation between compression/expansion and  
heating/cooling.

It is well-known that such correlations can lead to pulsational
instabilities in stars \citep{cox67}. We thus interpret  
dust-drag instabilities in a similar way, 
adapting from the treatment of stellar 
pulsations by \cite{cox67} and lecture notes by \cite{samadi15} and 
J. Christensen-Dalsgaard\footnote{\url{http://astro.phys.au.dk/$\sim$jcd/oscilnotes/}}.

@@

The physical interpretation of Eq. \ref{thermal_instability} is that 
work done by pressure forces in the dusty gas leads to growth in
oscillation amplitudes. To see this, we first compute the work done
assuming periodic oscillations. We then show that if the work done is positive, then the
oscillation amplitude in fact grows: the work done leads the
system to `overshoot' its equilibrium.

The average rate of work done is 
\begin{align}
  \mathcal{W} = \frac{1}{T_p}\int^{t+T_p}_{t}dt^\prime\int_M P
  \frac{Dv}{Dt^\prime} dm \label{work_def} 
\end{align}
\citep{cox67}, 
where $T_p$ is the oscillation period, $v=1/\rho$ is the specific
volume of the mixture, and the spatial integral is taken over the
total mass $M$ of the mixture and $dm$ is the mass element. 
Noting that only products of perturbations contribute to
$\mathcal{W}$, we find that for periodic oscillations (time dependence 
$e^{\ii\omega t}$ and real $\omega$): 
\begin{align}
  \mathcal{W} = - \frac{\omega}{2} \int \imag\left(\Delta P
  \frac{\Delta \rho^*}{\rho}\right)dV,\label{work_real}
\end{align}
where %the integral is taken over the volume of the
%mixture; and 
 the Lagragian perturbation $\Delta$ of a variable $f$ is 
$\Delta f = \delta f + \bm{\xi}\cdot\nabla f$; where $\bm{\xi}$ is the
Lagragian displacement ($    \xi_{x,z} =  \ii \dd v_{x,z}/\sigma$).  
Eq. \ref{work_real} show that a phase difference between gas pressure and
the total density leads to work done
($\mathcal{W}\neq0$).

Now, quite generally, Eq. \ref{lin_mass_full}---\ref{lin_energy_full} 
imply the integrand of the numerator in Eq. \ref{thermal_instability} 
is 
\begin{align} 
  \imag \left(\delta \mathcal{C}
  \nabla\cdot\dd \bm{v}^*\right) = 
  -|\sigma|^2\imag \left(\Delta P 
  \frac{\Delta\rho^*}{\rho}\right). \label{pdv}
\end{align}
%This states that `PdV' work (the right-hand-side) is 
%provided by dust-drag friction, and can be seen explicitly as 
%follows. 
Then combining Eq. \ref{work_real}, \ref{pdv} and
\ref{thermal_instability} 
gives  
\begin{align}
s = \frac{1}{\mathcal{I}^2}\mathcal{W}, \label{growth_work}
\end{align}
where we have set $\sigma= - \omega$ in 
Eq. \ref{pdv}. Eq. \ref{growth_work} shows that if the average work
done is positive during a periodic oscillation, $\mathcal{W}>0$, then
then its amplitude would actually grow ($s>0$).

To see when/where positive work is done, 
consider a point in the volume. We set $\Delta\rho = 1$ here 
and take $\omega>0$ without loss of generality. (Thus the phase of
perturbations increase in time.) This point contributes to positive
work done if $-\omega \imag\left(\Delta
P\Delta\rho^*\right)>0$, which requires $\imag\left(\Delta
P\right)<0$. This corresponds to pressure lagging behind density since
$\imag\left(\Delta\rho\right)=0$.

\subsubsection{Physical picture of dust-drag instabilities}

%We now use physical arguments to show that $\mathcal{W}>0$ if pressure
%perturbations (from the gas) lags behind the total density of the gas
%plus dust mixture. 
%The full energy equation is  
%\begin{align*}
%  \frac{DP}{Dt} = \frac{P}{\rho}\frac{D\rho}{D t} + \mathcal{C}. 
%\end{align*} 
%Dust-drag causes a phase difference between the pressure and density 
%evolution of a fluid element.

Fig. \ref{pdv_cartoon} gives a graphical demonstration that 
if gas pressure lags behind total density, then positive work done 
($\mathcal{W}>0$) because it leads to a clockwise path in the
`P-V' plane. Consider a fluid element at maximum density during an
oscillation cycle (point $A$), so that $D\rho/ D t = 0$. If dust-gas
drag provides an effective heating to the fluid element at $A$
(i.e. gas influx)  then it will experience increasing pressure, $DP/D
t>0$. It attains pressure maximum (point $B$) \emph{after} reaching
density maximum.    
From $A$ to $B$, pressure forces increase while the parcel is already
expanding. This corresponds to positive work done.

\begin{figure}
  \includegraphics[width=\linewidth]{figures/drag}\\
\includegraphics[width=\linewidth]{figures/pdv}
  \caption{Thermodynamic interpretation of overstable modes caused by
    dust-gas drag. Top: pressure and density evolution in time. 
    Bottom: oscillation cycle in the P-V plane. In the case shown,
    dust-drag causes 
    pressure to lag behind density, which results in a clockwise path in
    the P-V plane, implying positive work done by the fluid and
    hence would lead to growing oscillation amplitudes.  
    \label{pdv_cartoon}
  }
\end{figure}

This thermodynamic interpretation does not explain
\emph{why} dust drag causes pressure to lag behind density, but merely shows
that this \emph{must} be the case for any growing modes associated the
dust drag. To rigorously understand how dust-drag causes this
lag requires an explicit solution to the linearized equations with
detailed treatment of the function $\mathcal{C}$. However, given the complexity of
$\mathcal{C}$ (see Appendix \ref{lin_dust}), we might generally expect
the dusty disks to  support a range of stable and unstable modes, with the
latter being associated with pressure-density lag.

Indeed, \cite{jacquet11} explains the essence of the streaming 
instability in dusty protoplanetary disks as dust accumulation
(and hence compression) at a pressure bump, which then drags the 
gas towards it (and hence heating) to strengthen the pressure
bump. That is, heating occurs upon compression, as in stellar  
pulsational instabilities. In \S\ref{si} we check that the
streaming instability fits into this thermodynamic interpretation in
the strong drag limit.

%A phase difference was also noted in the 
%numerical calculations of the streaming instability by 
%\citet{youdin07b}.

@@

\subsection{Locally isothermal gas perfectly coupled to dust}\label{dusty_vsi_int}
If $c_s(r,z)$ is non-uniform but $\tstop=0$, Eq. \ref{int_rel} 
gives  
\begin{align}
%  s = \frac{\imag\int P
%  \left(\nabla\cdot\dd\bm{v}^*\right)\left(\dd\bm{v}\cdot\nabla\ln{c_s^2}\right)dV}{2\omega\int\rho\left(|\dd 
%    v_r|^2 + |\dd v_z|^2\right)dV}. \label{vsi_check} 
  s = \frac{\imag\int P
    \left(\nabla\cdot\dd\bm{v}^*\right)\left(\dd\bm{v}\cdot\nabla\ln{c_s^2}\right)dV}{2\omega\mathcal{I}^2}. \label{vsi_check} 
\end{align} 
This is VSI caused by vertical shear arising from a radial
temperature gradient \citep{nelson13,barker15,lin15}. We present 
numerical solutions of the VSI with perfectly-coupled dust in \S\ref{results}.
